### 2021-12-09 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@98b1970dc36f98ab33c18892639da1d76f72e072 🚀
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@441ee81db40c91c7be292d5e6cc0a92498cba381 🚀

Assuming a no-skill unbiased classifier (\emph{i.e.}
\(\mathbf{C}=\mathbf{M}\)), the accuracy is \(\rho^2 + (1-\rho)^2\), the
balanced accuracy is \(0.5\), Youden's J is \(0\), and \(F_1=\rho\). In
other words, given a connectance \(\rho = 0.05\), we expect that a
classifier guessing at random would still achieve an accuracy of
\(0.905\); for a connectance of \(\rho = 0.01\), this accuracy
\emph{increases} to over \(0.98\). In other words, networks with fewer
interactions have inherently higher accuracy, because it is easy to
predict the overwheling majority of non-interactions right.

@@

>>>>

Assuming a no-skill unbiased classifier (\(s=0.5\), \emph{i.e.}
\(\mathbf{C}=\mathbf{M}\) after normalization), the accuracy is
\(\rho^2 + (1-\rho)^2\), the balanced accuracy is \(0.5\), Youden's J is
\(0\), and \(F_1=\rho\). In other words, given a connectance
\(\rho = 0.05\), we expect that a classifier guessing at random would
still achieve an accuracy of \(0.905\); for a connectance of
\(\rho = 0.01\), this accuracy \emph{increases} to over \(0.98\). In
other words, networks with fewer interactions have inherently higher
accuracy, because it is easy to predict the overwheling majority of
non-interactions right.

@@

\hypertarget{what-are-the-baseline-values-of-thresholding-performance}{%
\subsection{What are the baseline values of thresholding
performance?}\label{what-are-the-baseline-values-of-thresholding-performance}}

ROC-AUC v. PR-AUC, vary \(s\) to simulate a classifier ranging from
no-skill to perfect
